Global study of well-being and internet adoption | Online analysis supplement

### 2021-11-18 03-analysis.Rmd
More ppc and plots

@@

```{r}

tmp_coefs <- fits_1c %>% 
  mutate(
    out = map(
      fit, 
      ~hypothesis(
        .x, 
        # Rescale coefficient here to years on %
        c(str_glue("val_year = 0")),
        scope = "coef",
        group = "region"
      )$hypothesis
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  mutate(result = str_glue('**{Estimate}** [{CI.Lower}, {CI.Upper}]')) %>% 
  select(cause, region = Group, result)
tmp_coefs
pseudo_gwp <-
  bind_rows(
    distinct(gbd, region, year, val = NA) %>% 
      crossing(
        cause = fct_inorder(
          c(
            "Negative\nexperiences", 
            "Positive\nexperiences", 
            "Life\nsatisfaction"
          )
        )
      )
  )

@@

# Draw small multiples figure, outcomes x regions
dat_all %>% 
  mutate(year = make_date(year)) %>% 
  ggplot(aes(year, mean)) +
  scale_y_continuous(
    "Value",
    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
    breaks = pretty_breaks()
  ) +
  scale_x_date(
    "Year",
    breaks = make_date(c(2000, 2005, 2010, 2015)), 
    date_labels = "'%y", 
    expand = expansion(.02)
  ) +
  geom_line(
    aes(group = interaction(country, cause)), 
    alpha = .25, size = .4, color = "dodgerblue1"
  ) +
  stat_summary(
    fun = mean, geom = "line", 
    size = .6, color = "dodgerblue4"
  ) +
  facet_grid(cause~region, scales = "free_y") +
  theme(
    legend.position = "none",
    panel.spacing = unit(3, "pt")
  ) +
  geom_richtext(
    data = tmp_coefs %>% mutate(cause = fct_inorder(str_to_title(cause))),
    aes(x = make_date(2000), y = Inf, label = result),
    size = 2.2, vjust = .9, hjust = 0.1, color = "dodgerblue4",
    family = Font,
    fill = NA, label.color = NA
  )
```

@@

  # Plot
  country_coefs %>% 
    ggplot(aes(internet, outcome)) +
    geom_path(
      data = country_ellipse,
      aes(x = x, y = y), 
      alpha = .2, size = .1, col = "dodgerblue1"
    ) +
    geom_vline(xintercept = 0, lty = 2, size = .2) +
    geom_hline(yintercept = 0, lty = 2, size = .2) +
    geom_point(col = "dodgerblue1", size = 1, alpha = .5) +
    scale_x_continuous(
      "Internet trend",
      breaks = pretty_breaks()
    ) +
    scale_y_continuous(
      breaks = pretty_breaks()
    ) +
    annotate(
      "text",
      x = Inf, y = Inf, label = country_cor_result,
      size = 4, vjust = 1.5, hjust = 1.05, color = "dodgerblue4",
      family = Font
    )
}
```

```{r}
draw_scatterplot(fits_1c$fit[[1]]) + labs(y = "Anxiety trend")
draw_scatterplot(fits_1c$fit[[2]]) + labs(y = "Depression trend")
draw_scatterplot(fits_1c$fit[[3]]) + labs(y = "Self-harm trend")
```

```{r}
p_time_main_correlations <- (p_cor_country_anx |
                               p_cor_country_dep |
                               p_cor_country_sel)

(wrap_elements(grid::textGrob('Negative experiences\nTBD')) |
    wrap_elements(grid::textGrob('Positive experiences\nTBD')) |
    wrap_elements(grid::textGrob('Life satisfaction\nTBD'))) /
  p_time_main_correlations

p_time_main_coefs /
  p_time_main_correlations
```

```{r time-correlation-depression}
# Get average and region
r_region_depression <- fit_dep %>% 
  spread_draws(
    b_Depression_time, 
    b_internet_time,
    r_region__Depression[region, term],
    r_region__internet[region, term]
  ) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  # Fix names by replacing dot with line break
  mutate(region = str_replace(region, "\\.", "\n"))

# Then country
r_country_depression <- fit_dep %>% 
  spread_draws(
    r_country__Depression[country, term],
    r_country__internet[country, term]
  ) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  # Fix names by taking labels from original names
  mutate(
    country = factor(
      country, 
      labels = sort(unique(fit_dep$data$country))
    )
  ) %>% 
  left_join(distinct(dat, region, country))

# Calculate country coefficients
country_depression <- left_join(r_country_depression, r_region_depression) %>% 
  mutate(
    internet = b_internet_time + r_region__internet + r_country__internet,
    depression = b_Depression_time + r_region__Depression + r_country__Depression
  ) %>% 
  group_by(country, region) %>% 
  median_qi(internet, depression)

country_depression_ellipse <- spread_draws(
  fit_dep,
  b_Depression_time, b_internet_time,
  cor_country__internet_time__Depression_time, 
  ndraws = 100
) %>% 
  mutate(
    e = pmap(
      list(
        x = cor_country__internet_time__Depression_time, 
        y = b_internet_time, 
        z = b_Depression_time
      ), 
      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
        as_tibble()
    )
  ) %>% 
  unnest(e)

region_depression_ellipse <- spread_draws(
  fit_dep,
  b_Depression_time, b_internet_time,
  cor_region__internet_time__Depression_time, 
  ndraws = 100
) %>% 
  mutate(
    e = pmap(
      list(
        x = cor_region__internet_time__Depression_time, 
        y = b_internet_time, 
        z = b_Depression_time
      ), 
      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
        as_tibble()
    )
  ) %>% 
  unnest(e)

country_depression_cor <- fit_dep %>%
  as_draws_df(
    variable = c(
      "cor_country__internet_time__Depression_time",
      "cor_region__internet_time__Depression_time"
    ),
    regex = TRUE
  ) %>% 
  as_tibble()
country_depression_result <- country_depression_cor %>%   
  summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95))) %>% 
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  mutate(result = str_glue("{`50%`} [{`5%`}, {`95%`}]"))

p_cor_country_dep <- country_depression %>% 
  ggplot(aes(internet, depression)) +
  # geom_path(
  #   data = region_depression_ellipse, 
  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue4"
  # ) +
  # geom_path(
  #   data = country_depression_ellipse, 
  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue1"
  # ) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_hline(yintercept = 0, lty = 2, size = .2) +
  geom_point(col = "dodgerblue1", size = 1, alpha = .75) +
  scale_x_continuous(
    "Linear internet trend",
    breaks = pretty_breaks()
  ) +
  scale_y_continuous(
    "Linear depression trend",
    breaks = pretty_breaks()
  ) +
  geom_richtext(
    data = country_depression_result %>% 
      filter(variable == "cor_country__internet_time__Depression_time"),
    aes(x = -Inf, y = Inf, label = result),
    size = 3, vjust = 1, hjust = -0.1, color = "dodgerblue4",
    family = Font,
    fill = NA, label.color = NA
  ) +
  theme(aspect.ratio = 1)
```

```{r time-correlation-selfharm}
# Get average and region
r_region_selfharm <- fit_sel %>% 
  spread_draws(
    b_Selfharm_time, 
    b_internet_time,
    r_region__Selfharm[region, term],
    r_region__internet[region, term]
  ) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  # Fix names by replacing dot with line break
  mutate(region = str_replace(region, "\\.", "\n"))

# Then country
r_country_selfharm <- fit_sel %>% 
  spread_draws(
    r_country__Selfharm[country, term],
    r_country__internet[country, term]
  ) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  # Fix names by taking labels from original names
  mutate(
    country = factor(
      country, 
      labels = sort(unique(fit_sel$data$country))
    )
  ) %>% 
  left_join(distinct(dat, region, country))

# Calculate country coefficients
country_selfharm <- left_join(r_country_selfharm, r_region_selfharm) %>% 
  mutate(
    internet = b_internet_time + r_region__internet + r_country__internet,
    selfharm = b_Selfharm_time + r_region__Selfharm + r_country__Selfharm
  ) %>% 
  group_by(country, region) %>% 
  median_qi(internet, selfharm)

country_selfharm_ellipse <- spread_draws(
  fit_sel,
  b_Selfharm_time, b_internet_time,
  cor_country__internet_time__Selfharm_time, 
  ndraws = 100
) %>% 
  mutate(
    e = pmap(
      list(
        x = cor_country__internet_time__Selfharm_time, 
        y = b_internet_time, 
        z = b_Selfharm_time
      ), 
      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
        as_tibble()
    )
  ) %>% 
  unnest(e)

region_selfharm_ellipse <- spread_draws(
  fit_sel,
  b_Selfharm_time, b_internet_time,
  cor_region__internet_time__Selfharm_time, 
  ndraws = 100
) %>% 
  mutate(
    e = pmap(
      list(
        x = cor_region__internet_time__Selfharm_time, 
        y = b_internet_time, 
        z = b_Selfharm_time
      ), 
      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
        as_tibble()
    )
  ) %>% 
  unnest(e)

country_selfharm_cor <- fit_sel %>%
  as_draws_df(
    variable = c(
      "cor_country__internet_time__Selfharm_time",
      "cor_region__internet_time__Selfharm_time"
    ),
    regex = TRUE
  ) %>% 
  as_tibble()
country_selfharm_result <- country_selfharm_cor %>%   
  summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95))) %>% 
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  mutate(result = str_glue("{`50%`} [{`5%`}, {`95%`}]"))

p_cor_country_sel <- country_selfharm %>% 
  ggplot(aes(internet, selfharm)) +
  # geom_path(
  #   data = region_selfharm_ellipse, 
  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue4"
  # ) +
  # geom_path(
  #   data = country_selfharm_ellipse, 
  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue1"
  # ) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_hline(yintercept = 0, lty = 2, size = .2) +
  geom_point(col = "dodgerblue1", size = 1, alpha = .75) +
  scale_x_continuous(
    "Linear internet trend",
    breaks = pretty_breaks()
  ) +
  scale_y_continuous(
    "Linear selfharm trend",
    breaks = pretty_breaks()
  ) +
  geom_richtext(
    data = country_selfharm_result %>% 
      filter(variable == "cor_country__internet_time__Selfharm_time"),
    aes(x = -Inf, y = Inf, label = result),
    size = 3, vjust = 1, hjust = -0.1, color = "dodgerblue4",
    family = Font,
    fill = NA, label.color = NA
  ) +
  theme(aspect.ratio = 1)
```

```{r}
p_cor_country_anx + theme(axis.title.x = element_blank()) | 
  p_cor_country_dep | 
  p_cor_country_sel + theme(axis.title.x = element_blank())
```

>>>>

```{r}
pp_check(
  fits_1c$fit[[1]], 
  ndraws = 30, 
  resp = "internet", 
  newdata = fits_1c$fit[[1]]$data
  )

pp_check(
  fits_1c$fit[[1]], 
  ndraws = 10, 
  type = "dens_overlay_grouped",
  group = "region",
  resp = "val", 
  newdata = fits_1c$fit[[1]]$data
)
```

@@

```{r}
tmp_coefs <- fits_1c %>% 
  mutate(
    out = map(
      fit, 
      ~hypothesis(
        .x, 
        # Rescale coefficient here to years on %
        c(str_glue("val_year = 0")),
        scope = "coef",
        group = "region"
      )$hypothesis
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  mutate(result = str_glue('**{Estimate}** [{CI.Lower}, {CI.Upper}]')) %>% 
  select(cause, region = Group, result)
tmp_coefs
pseudo_gwp <-
  bind_rows(
    distinct(gbd, region, year, val = NA) %>% 
      crossing(
        cause = fct_inorder(
          c(
            "Negative\nexperiences", 
            "Positive\nexperiences", 
            "Life\nsatisfaction"
          )
        )
      )
  )

@@

# Draw small multiples figure, outcomes x regions
dat_all %>% 
  mutate(year = make_date(year)) %>% 
  ggplot(aes(year, mean)) +
  scale_y_continuous(
    "Value",
    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
    breaks = pretty_breaks()
  ) +
  scale_x_date(
    "Year",
    breaks = make_date(c(2000, 2005, 2010, 2015)), 
    date_labels = "'%y", 
    expand = expansion(.02)
  ) +
  geom_line(
    aes(group = interaction(country, cause)), 
    alpha = .25, size = .4, color = "dodgerblue1"
  ) +
  stat_summary(
    fun = mean, geom = "line", 
    size = .6, color = "dodgerblue4"
  ) +
  facet_grid(cause~region, scales = "free_y") +
  theme(
    legend.position = "none",
    panel.spacing = unit(3, "pt")
  ) +
  geom_richtext(
    data = tmp_coefs %>% mutate(cause = fct_inorder(str_to_title(cause))),
    aes(x = make_date(2000), y = Inf, label = result),
    size = 2.4, vjust = .9, hjust = 0.05, color = "dodgerblue4",
    family = Font,
    fill = NA, label.color = NA
  )
```

@@

  # Plot
  country_coefs %>% 
    ggplot(aes(internet, outcome)) +
    geom_path(
      data = country_ellipse,
      aes(x = x, y = y, group = .draw), 
      alpha = .2, size = .1, col = "dodgerblue1"
    ) +
    geom_vline(xintercept = 0, lty = 2, size = .2) +
    geom_hline(yintercept = 0, lty = 2, size = .2) +
    geom_point(col = "dodgerblue1", size = 1, alpha = .5) +
    scale_x_continuous(
      "Internet trend",
      breaks = pretty_breaks()
    ) +
    scale_y_continuous(
      breaks = pretty_breaks()
    ) +
    annotate(
      "text",
      x = Inf, y = Inf, label = country_cor_result,
      size = 4, vjust = 1.5, hjust = 1.05, color = "dodgerblue4",
      family = Font
    )
}
```

```{r}
p1 <- draw_scatterplot(fits_1c$fit[[1]]) + labs(y = "Anxiety trend")
p2 <- draw_scatterplot(fits_1c$fit[[2]]) + labs(y = "Depression trend")
p3 <- draw_scatterplot(fits_1c$fit[[3]]) + labs(y = "Self-harm trend")
```

```{r}
(wrap_elements(grid::textGrob('Negative experiences\nTBD')) |
    wrap_elements(grid::textGrob('Positive experiences\nTBD')) |
    wrap_elements(grid::textGrob('Life satisfaction\nTBD'))) /
  (p1 | p2 | p3)
```
